On the Social Compatibility of Genome Analysis

### 2022-06-16 draft.tex
conclusion tweak

\subsection{Commercial Aspect of Identity}
DNA tests are more popular than ever. 
In 2018, the global direct-to-consumer genetic test market was valued at just over 800 million USD and is estimated to grow to around 6.3 billion USD by 2028. This is more than an estimated sevenfold increase over a 10-year period.
There are multiple reasons responsible for bolstering the industry demand.

@@

In general, every user of DNA tests should be informed about what can be read from the data, what is stored and then decide whether the added value outweighs the potential risk of a leak in his or her individual case.
On condition that the person is given the opportunity to make a choice.

@@

>>>>

\subsection{Identity Marketing}
DNA tests are more popular than ever. 
In 2018, the global direct-to-consumer genetic test market was valued at just over 800 million USD and is estimated to grow to around 6.3 billion USD by 2028. This is more than an estimated sevenfold increase over a 10-year period.
There are multiple reasons responsible for bolstering the industry demand.

@@

In general, every user of DNA tests should be informed about what can be derived from the data, what is stored and then decide whether the added value outweighs the potential risk of a leak in his or her individual case.
On condition that the person is given the opportunity to make a choice.

@@

In the chapter Analysis we provided the example of unethical technological abuse in the insurance sector, illuminating why more information being public is not always beneficial and pointed to legal action being taken to prevent this.
